Semi-Permeable Vesicles: Mathematical Formulation, Numerics, and Physics

### 2020-12-08 vesicle_code/docs/permeableVes/main.tex
edits to figs
working on parabolic example

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Poiseuille Flow}
\begin{figure}[htp]
  \ifTikz
  \input{figures/parabolicComposite.tikz}
  \fi
  \caption{\label{fig:parabolicComposite} (a) The steady-state shape of
  an impermeable vesicle submerged in a Poiseuille flow with varying
  initial reduced areas and flow rates. The results agree with Kaoui et
  al.~\cite{kao-bir-mis2009}. (b) The steady state shape of a
  semi-permeable vesicle submerged in a Poiseuille flow with varying
  initial reduced areas and flow rates.}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Poiseuille Flow}
\begin{figure}[htp]
%  \ifTikz
  \input{figures/parabolicComposite.tikz}
%  \fi
  \caption{\label{fig:parabolicComposite} (a) The steady state shape of a
  semi-permeable vesicle submerged in a Poiseuille flow with varying
  initial reduced areas and flow rates. (b) The steady-state inclination
  angle for four different flow velocities. The steady-state shapes are
  superimposed. (c) The reduced area of the slipper formed with the
  flow rate of 800 $\mu m/s$. (d) The vesicle shape shown with the
  background imposed flow. The channel width is 12.5 times larger than
  the vesicle radius. The corresponding reduced area for each shape is
  indicated by the marks in plot (c).}
\end{figure}
